The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-02-24 code/MADAprojectcode.qmd
Doc

>>>>

```{r}
#| label: fig-schematic
#| fig-cap: "Workflow schematic for analyzing associations between malaria during pregnancy, treatment regimens, and health outcomes."
#| echo: FALSE
#| screenshot.force: TRUE  # This forces a screenshot to be taken

library(DiagrammeR)

grViz("
  digraph statistical_workflow {
    node [shape = rectangle, style = filled, fillcolor = lightblue]

    Data_Collection [label = 'Data Collection']
    Data_Cleaning [label = 'Data Cleaning & Preprocessing']
    Exploratory_Analysis [label = 'Exploratory & Descriptive Analysis']
    Statistical_Tests [label = 'Inferential Analysis\\n(Logistic, Poisson, Chi-Square)']
    Sensitivity_Analyses [label = 'Sensitivity Analyses']
    Results_Reporting [label = 'Reporting & Visualization']

    Data_Collection -> Data_Cleaning -> Exploratory_Analysis -> Statistical_Tests -> Sensitivity_Analyses -> Results_Reporting
  }
")

### 2025-02-24 products/manuscript/Manuscript.qmd
Doc

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

The structure below is one possible setup for a manuscript, or a general data analysis project (including the course project). Adjust as needed.

You don't need to have exactly these sections, but the content covering those sections should be addressed.

This uses MS Word as output format. [See here](https://quarto.org/docs/output-formats/ms-word.html) for more information. You can switch to other formats, like html or pdf. See [the Quarto documentation](https://quarto.org/) for other formats.

```{r}
# Loading necessary libraries
library(tidyverse)
library(janitor)
library(knitr)
library(lubridate)
library(readr)
library(here)
```

@@

```{r}
#| label: fig-schematic
#| fig-cap: "Workflow schematic for analyzing associations between malaria during pregnancy, treatment regimens, and health outcomes."
#| echo: FALSE

library(DiagrammeR)

grViz("
  digraph statistical_workflow {
    node [shape = rectangle, style = filled, fillcolor = lightblue]

    Data_Collection [label = 'Data Collection']
    Data_Cleaning [label = 'Data Cleaning & Preprocessing']
    Exploratory_Analysis [label = 'Exploratory & Descriptive Analysis']
    Statistical_Tests [label = 'Inferential Analysis\\n(Logistic, Poisson, Chi-Square)']
    Sensitivity_Analyses [label = 'Sensitivity Analyses']
    Results_Reporting [label = 'Reporting & Visualization']

    Data_Collection -> Data_Cleaning -> Exploratory_Analysis -> Statistical_Tests -> Sensitivity_Analyses -> Results_Reporting
  }
")

```

@@

```{r}
# Print the root directory to confirm the correct path
print(here())

# Read the CSV file using here()
PROMO_Data <- read_csv(here("PROMO_Data.csv"))

# View the dataset
View(PROMO_Data)

```

```{r}
#3. Initial Data Inspection
# View structure of the dataset
str(PROMO_Data)

# View first few rows
head(PROMO_Data)

# Check column names
colnames(PROMO_Data)

# Get summary statistics
summary(PROMO_Data)

# Count missing values in each column
colSums(is.na(PROMO_Data))
```

@@

*Use a combination of text/tables/figures to explore and describe your data. Show the most important descriptive results here. Additional ones should go in the supplement. Even more can be in the R and Quarto files that are part of your project.*

@tbl-summarytable shows a summary of the data.

@@

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

@@

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

>>>>

---
title: "The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women"
author: "Asmith Joseph"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
    prefer-html: true
    reference-location: margin  # Enable reference links
knitr:
  opts_chunk:
    screenshot.force: TRUE
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

@@

@@

@@

@@

@@
